```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidymodels)
library(ranger)
library(topicmodels)
library(readr)
library(tidyverse)
library(lubridate)
library(dplyr)
library(tidytext)
library(rtweet)
library(readxl)
library(janitor)
library(devtools)
library(Rcpp)
library(vip)
library(reshape2)
library(corrplot)
library(MASS)
library(skimr)
library(VIF)
library(fastDummies)
```

```{r}
boston <- read_csv("boston.csv")
zips <- read_csv("zips.csv") %>%
  mutate(ZIP = as.character(ZIP)) %>%
  mutate(ZIP = str_sub(ZIP, 2,5)) %>%
  mutate(ZIP = as.numeric(ZIP))
```

## Explore Target  

```{r}
boston %>%
  summarize(mean(AV_TOTAL))
boston %>%
  ggplot(aes(AV_TOTAL)) +
  geom_histogram() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "", x = "", y = "")
boston %>%
  ggplot(aes(AV_TOTAL)) +
  geom_boxplot() +
  coord_flip() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "", x = "", y = "")
```

## Home-age variable 
##  - IF yr_remod > yr_built THEN age = 2020 - yr_remod
##  - ELSE age = 2020 - yr_built

```{r}
transformed_data <- zips %>%
  inner_join(boston, zips, by = c("ZIP"="ZIPCODE")) %>%
  mutate(HOME_AGE = if_else(YR_REMOD > YR_BUILT, 2020 - YR_REMOD, 2020 - YR_BUILT, missing = NULL))
```

## Explore Numeric Predictors 

```{r}
options(scipen = 10)

histogram <- function(df, x, ...) {
  ggplot(df) +
    geom_histogram(mapping = aes(x = df[[x]], ...)) +
    labs(title = paste(x, "distribution"), x = x)
}

AV_TOTAL_hist <- histogram(transformed_data, "AV_TOTAL")
AV_TOTAL_hist

LAND_SF_hist <- histogram(transformed_data, "LAND_SF")
LAND_SF_hist

LIVING_AREA_hist <- histogram(transformed_data, "LIVING_AREA")
LIVING_AREA_hist

HOME_AGE_hist <- histogram(transformed_data, "HOME_AGE")
HOME_AGE_hist

logarithmic_histogram <- function(df, x, ...) {
  ggplot(df) +
    geom_histogram(mapping = aes(x = log(df[[x]]), ...)) +
    labs(title = paste(x, "distribution"), x = x)
}

AV_TOTAL_log <- logarithmic_histogram(transformed_data, "AV_TOTAL")
AV_TOTAL_log

LAND_SF_log <- logarithmic_histogram(transformed_data, "LAND_SF")
LAND_SF_log

LIVING_AREA_log <- logarithmic_histogram(transformed_data, "LIVING_AREA")
LIVING_AREA_log

HOME_AGE_log <- logarithmic_histogram(transformed_data, "HOME_AGE")
HOME_AGE_log

transformed_data %>%
  group_by(City_State, na.rm = TRUE) %>%
  ggplot(aes(x = reorder(City_State, -AV_TOTAL), y = AV_TOTAL)) +
  geom_bar(mapping = NULL, stat = "identity", position = "stack") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "City & State Name", y = "AV_TOTAL")
```

## Correlations 

```{r}
transformed_data %>%
  filter(!is.na(AV_TOTAL)) %>%
  filter(!is.na(LAND_SF)) %>%
  filter(!is.na(LIVING_AREA)) %>%
  filter(!is.na(HOME_AGE)) %>%
  filter(!is.na(City_State))

transformed_subset <- subset(transformed_data, select = c("AV_TOTAL", "LAND_SF", "LIVING_AREA", "HOME_AGE"))

transformed_subset %>%
  filter(!is.na(LAND_SF)) %>%
  na.omit() %>%
  cor() 
transformed_subset %>%
  na.omit() %>%
  cor() %>%
  melt %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(mid = "#FBFEF9", low = "#0C6291", high = "#A63446") +
  geom_text(aes(label = round(value, 3)), color = "black")
```


## Explore Categorical Predictors 

```{r}
options(scipen = 10)

transformed_data %>%
  group_by(City_State) %>%
  summarize(mean_AV_TOTAL = mean(AV_TOTAL)) %>%
  ggplot(aes(x = reorder(City_State, -mean_AV_TOTAL), y = mean_AV_TOTAL)) +
  geom_bar(mapping = NULL, stat = "identity", position = "stack") +
  geom_hline(aes(yintercept = mean(mean_AV_TOTAL))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "AV_TOTAL by City and State", x = "Name of City and State", y = "AV_TOTAL")
transformed_data %>%
  group_by(R_BLDG_STYL) %>%
  summarize(mean_AV_TOTAL = mean(AV_TOTAL)) %>%
  ggplot(aes(x = reorder(R_BLDG_STYL, -mean_AV_TOTAL), y = mean_AV_TOTAL)) +
  geom_bar(mapping = NULL, stat = "identity", position = "stack") +
  geom_hline(aes(yintercept = mean(mean_AV_TOTAL))) +
  theme(axis.text.x = element_text(hjust = 1)) +
  labs(title = "AV_TOTAL by Building Style", x = "", y = "AV_TOTAL")
transformed_data %>%
  group_by(R_INT_CND) %>%
  summarize(mean_AV_TOTAL = mean(AV_TOTAL)) %>%
  ggplot(aes(x = reorder(R_INT_CND, -mean_AV_TOTAL), y = mean_AV_TOTAL)) +
  geom_bar(mapping = NULL, stat = "identity", position = "stack") +
  geom_hline(aes(yintercept = mean(mean_AV_TOTAL))) +
  theme(axis.text.x = element_text(hjust = 1)) +
  labs(title = "AV_TOTAL by Interior Condition", x = "Interior Condition", y = "AV_TOTAL")
transformed_data %>%
  group_by(R_OVRALL_CND) %>%
  summarize(mean_AV_TOTAL = mean(AV_TOTAL)) %>%
  ggplot(aes(x = reorder(R_OVRALL_CND, -mean_AV_TOTAL), y = mean_AV_TOTAL)) +
  geom_bar(mapping = NULL, stat = "identity", position = "stack") +
  geom_hline(aes(yintercept = mean(mean_AV_TOTAL))) +
  theme(axis.text.x = element_text(hjust = 1)) +
  labs(title = "AV_TOTAL by Overall condition of Home", x = "Overall Condition", y = "AV_TOTAL")
```

### Prep data 
## mutate_at(c("var1", ...), as.factor)

```{r}
prep_data <- transformed_data %>%
  subset(select = c("PID", "AV_TOTAL", "HOME_AGE", "LAND_SF", "LIVING_AREA", "NUM_FLOORS", "Population", "Median_Income", "City_State", "R_INT_CND", "R_BLDG_STYL", "R_OVRALL_CND", "R_KITCH_STYLE")) %>%
  mutate_at(c("City_State", "R_INT_CND", "R_BLDG_STYL", "R_OVRALL_CND", "R_KITCH_STYLE"), as.factor)
```

```{r}
set.seed(1000)
train_test_split <- initial_split(prep_data, prop = 0.7)

train <- training(train_test_split)
test <- testing(train_test_split)

nrow(train)/nrow(prep_data)
nrow(test)/nrow(prep_data)
```

## Recipe 

```{r}
recipe_spec <- recipe(AV_TOTAL ~ ., data = prep_data) %>%
  step_rm(PID) %>%
  step_impute_mean(all_numeric()) %>%
  step_log(all_numeric()) %>%
  step_impute_mode(all_nominal()) %>%
  step_dummy(all_nominal())
recipe_spec
```

## Bake

```{r}
bake_train <- bake(recipe_spec %>% prep(), train)
bake_test  <- bake(recipe_spec %>% prep(), test)
```

## Create and fit linear Regression & RF

logistic_reg <-  
  logistic_reg(mode = "regression") %>%   
  set_engine("lm") %>%  
  fit(av_total ~., data = bake_train)  
  
random_forest <-  
  rand_forest(trees=25) %>%
  set_mode("regression") %>%
  set_engine("ranger",  importance = "permutation") %>%
  fit(av_total ~., data = bake_train)


```{r}
linear_model <-  
  linear_reg(mode = "regression") %>%   
  set_engine("lm") %>%  
  fit(AV_TOTAL ~., data = bake_train)  
  
random_forest_model <-  
  rand_forest(trees = 25) %>%
  set_mode("regression") %>%
  set_engine("ranger",  importance = "permutation") %>%
  fit(AV_TOTAL ~., data = bake_train)
``` 

```{r}
glance(linear_model$fit)
tidy(linear_model$fit)
```

## Evaluation  

```{r}
scored_train_lm <- predict(linear_model, bake_train) %>% 
  mutate(.pred = exp(.pred)) %>% 
  bind_cols(train) %>%
  mutate(.res = AV_TOTAL - .pred, .model = "linear reg", .part  = "train")

scored_test_lm <- predict(linear_model, bake_test) %>%
  mutate(.pred = exp(.pred)) %>% 
  bind_cols(test) %>%
  mutate(.res = AV_TOTAL - .pred, .model = "linear reg", .part  = "test")

scored_train_rf <- predict(random_forest_model, bake_train) %>% 
  mutate(.pred = exp(.pred)) %>% 
  bind_cols(train) %>%
  mutate(.res = AV_TOTAL - .pred, .model = "random forest", .part  = "train")  
           
scored_test_rf <- predict(random_forest_model, bake_test) %>% 
  mutate(.pred = exp(.pred)) %>% 
  bind_cols(test) %>%
  mutate(.res = AV_TOTAL - .pred, .model = "random forest", .part  = "test")

model_evaluation <- bind_rows(scored_train_lm, scored_test_lm, scored_train_rf, scored_test_rf, id = NULL)
```

model_evaluation %>%
  group_by(.model, .part) %>%
    metrics(av_total, estimate = .pred) %>%
  pivot_wider(names_from = .metric, values_from = .estimate) %>%
  select(-.estimator)

model %>%
  vip(num_features = 20)

```{r}
model_evaluation %>%
  group_by(.model, .part) %>%
  metrics(AV_TOTAL, estimate = .pred) %>%
  pivot_wider(names_from = .metric, values_from = .estimate) %>%
  subset(select = c(".model", ".part", "rmse", "rsq", "mae"))

linear_model %>%
  vip(num_features = 20)

random_forest_model %>%
  vip(num_features = 20)
```
  
```{r}
linear_reg_test <- scored_test_lm  %>%
  filter(!is.na(HOME_AGE)) %>%
  mutate(.res = AV_TOTAL - .pred) %>%
  slice_max(abs(.res), n = 10) %>%
  arrange(desc(AV_TOTAL))
linear_reg_test

linear_reg_test <- scored_test_lm %>%
  filter(!is.na(HOME_AGE)) %>%
  mutate(.res = AV_TOTAL - .pred) %>%
  slice_min(abs(.res), n = 10) %>%
  arrange(desc(AV_TOTAL))
linear_reg_test

random_forest_test <- scored_test_rf %>%
  filter(!is.na(HOME_AGE)) %>%
  mutate(.res = AV_TOTAL - .pred) %>%
  slice_max(abs(.res), n = 10) %>%
  arrange(desc(AV_TOTAL))
random_forest_test

random_forest_test <- scored_test_rf %>%
  filter(!is.na(HOME_AGE)) %>%
  mutate(.res = AV_TOTAL - .pred) %>%
  slice_min(abs(.res), n = 10) %>%
  arrange(desc(AV_TOTAL))
random_forest_test
```



