---
title: "Churn Analysis"
by: Tyler Grosman
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(pROC)
library(caret)
library(tidyverse)
library(lubridate)
library(janitor)
library(skimr)
library(lubridate)
library(RSocrata)
library(tidyquant)
library(tidymodels)
library(ranger)
library(topicmodels)
library(readr)
library(tidyverse)
library(lubridate)
library(dplyr)
library(tidytext)
library(readxl)
library(janitor)
library(devtools)
library(Rcpp)
library(vip)
library(ggplot2)
library(corrplot)
library(corrr)
library(MASS)
library(VIF)
library(vip)
library(fastDummies)
library(kableExtra)
library(GGally)
library(kableExtra)
library(parallel)
library(doParallel)
library(fastshap)
library(rpart.plot)
library(ggpubr)
library(glmnet)     #lasso and regularization 
library(rpart.plot) #plotting decision trees 
library(reshape2)
```

```{r}
churn_training <- read_csv("Churn_training.csv", show_col_types = FALSE) %>%
  clean_names() %>%
  mutate(churn = as_factor(churn)) %>%
  mutate_if(is.character, as_factor)
churn_training %>%
  head()

churn_holdout <- read_csv("Churn_holdout.csv") %>%
  clean_names() %>%
  mutate_if(is.character, as_factor)
churn_holdout %>%
  head()
```

```{r}
#skim_without_charts(churn_training)
#skim_without_charts(churn_holdout)
```

```{r, message = FALSE, warning = FALSE}
options(yardstick.event_first = FALSE)
model_score <- function(churn_training, model, model_name) {
  scored_df <- predict(model, churn_training, type = "prob") %>%
    bind_cols(., predict(model, churn_training)) %>%
    bind_cols(churn_training) %>%
    mutate(model_name = model_name)
  
  return(scored_df)
}

accuracy_score <- function(train, test, model_name) {
  train %>%
    group_by(model_name) %>%
    bind_rows(test) %>%
    metrics(churn, estimate = .pred_class) %>%
    filter(.metric == "accuracy") %>%
    spread(.metric, .estimate) %>%
    dplyr::select(-.estimator) -> results1
  print(results1)
}
```

## Target Exploration 

```{r}
churn_training %>%
  count(churn) %>%
  mutate(pct = n/sum(n)) -> churn_rate

churn_rate

churn_training %>%
  group_by(churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) -> churn_rate

churn_training_plot <- ggtexttable(churn_rate, rows = NULL, 
                        theme = ttheme("mOrange"))

churn_rate %>%
  ggplot(aes(x = churn, y = n)) +
  geom_col() + labs("Churn Target Counts") -> p1

churn_rate %>%
  ggplot(aes(x = churn , y = pct)) +
  geom_col() + labs(title = "Churn Target") -> p2

ggarrange(p2, churn_training_plot, 
          ncol = 1, nrow = 2,
          heights = c(1, 0.3))

churn_cormat <- churn_training %>%
  mutate(churn = as.numeric(churn)) %>%
  select_if(is.numeric) %>%
  na.omit() %>%
  cor() %>%
  round(digits = 4) %>%
  melt()

churn_cormat %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(mid = "#FBFEF9",low = "#A63446",high = "#0C6291") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_text(aes(label = round(value, 3)), color = "blue")  
```

## Variable Exploration

```{r}
churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(monthly_minutes, fill = churn)) +
  geom_histogram(bins = 25, position = "fill") +
  labs(title = "monthly_minutes & churn") +
  ylab("pct") +
  xlab("monthly_minutes")

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(x = customer_service_calls, fill = churn)) +
  geom_bar() +
  labs(title = "customer_service_calls & churn") +
  ylab("Count") +
  xlab("customer_service_calls")

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(streaming_minutes, fill = churn)) +
  geom_histogram(bins = 25, position = "fill") +
  labs(title = "distribution of streaming_minutes & churn") +
  ylab("pct") +
  xlab("streaming_minutes")

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(total_billed, fill = churn)) +
  geom_histogram(bins = 75, position = "fill") +
  labs(title = "distribution of total_billed & churn") +
  ylab("Count") +
  xlab("total_billed")

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(prev_balance, fill = churn)) +
  geom_histogram(bins = 50, position = "fill") +
  labs(title = "distribution of prev_balance & churn") +
  ylab("Count") +
  xlab("prev_balance")

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(late_payments, fill = churn)) +
  geom_histogram(bins = 10, postion = "fill") +
  labs(title = "distribution of late_payments & churn") +
  ylab("Count") +
  xlab("late_payments")

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(phone_area_code, fill = churn)) +
  geom_histogram(bins = 50, position = "fill") +
  labs(title = "distribution of phone_area_code & churn") +
  ylab("Count") +
  xlab("phone_area_code")

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(x = number_phones, fill = churn)) +
  geom_histogram(bins = 10, position = "fill") +
  labs(title = "distribution of number_phones & churn") +
  ylab("Count") +
  xlab("number_phones")

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(x = senior_citizen, fill = churn)) +
  geom_bar() +
  labs(title = "distribution of  & churn") +
  ylab("Count") +
  xlab("senior_citizen")
```

## Scatterplots

```{r}
churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(x = total_billed, y = streaming_minutes, color = churn)) +
  geom_point()

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(x = customer_service_calls, y = number_phones, color = churn)) +
  geom_point() 

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(x = streaming_minutes, y = prev_balance, color = churn)) +
  geom_point() 

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(x = streaming_minutes, y = monthly_minutes, color = churn)) +
  geom_point() 

churn_training %>%
  mutate(churn = as.character(churn)) %>%
  ggplot(aes(x = total_billed, y = prev_balance, color = churn)) +
  geom_point() 
```

## Categorical Data 

```{r}
churn_training %>%
  group_by(phone_model, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_phone_model

frequency_table_phone_model

churn_training %>%
  group_by(phone_model, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = phone_model, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(phone_model, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(phone_model, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

## Email Domain

```{r}
churn_training %>%
  group_by(email_domain, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table

frequency_table

churn_training %>%
  group_by(email_domain, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = email_domain, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(email_domain, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(email_domain, pct), x = n, fill = churn)) + 
  geom_col(position = "fill")
```

## Billing Postal (NOT significant)

```{r}
churn_training %>%
  group_by(billing_postal, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_postal

frequency_table_postal

churn_training %>%
  group_by(billing_postal, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = billing_postal, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(billing_postal, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(billing_postal, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 

```

## Billing State (POSSIBLY significant)

```{r}
churn_training %>%
  group_by(billing_state, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_state

frequency_table_state

churn_training %>%
  group_by(billing_state, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = billing_state, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(billing_state, churn) %>%
  summarise(n = n()) %>%
  mutate(pct=n/sum(n)) %>%
  ggplot(aes(y = reorder(billing_state, pct), x = n, fill = churn)) + 
  geom_col(position="fill") 
```

## Streaming Plan

```{r}
churn_training %>%
  group_by(streaming_plan, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_streaming_plan

frequency_table_streaming_plan

churn_training %>%
  group_by(streaming_plan, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = streaming_plan, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(streaming_plan, churn) %>%
  summarise(n = n()) %>%
  mutate(pct=n/sum(n)) %>%
  ggplot(aes(y = reorder(streaming_plan, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

## Mobile Hotspot (NOT significant)

```{r}
churn_training %>%
  group_by(mobile_hotspot, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_hotspot

frequency_table_hotspot

churn_training %>%
  group_by(mobile_hotspot, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = mobile_hotspot, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(mobile_hotspot, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(mobile_hotspot, pct), x = n, fill = churn)) + 
  geom_col(position = "fill")
```

## Wifi Calling & Text (NOT significant)

```{r}
churn_training %>%
  group_by(wifi_calling_text, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_wct

frequency_table_wct

churn_training %>%
  group_by(wifi_calling_text, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = wifi_calling_text, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(wifi_calling_text, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(wifi_calling_text, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

## Device Protection

```{r}
churn_training %>%
  group_by(device_protection, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_protection

frequency_table_protection

churn_training %>%
  group_by(device_protection, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = device_protection, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(device_protection, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(device_protection, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

## Contract Code (NOT significant)

```{r}
churn_training %>%
  group_by(contract_code, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_contract

frequency_table_contract

churn_training %>%
  group_by(contract_code, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = contract_code, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(contract_code, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(contract_code, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

## Currency Code (SIGNIFICANT)

```{r}
churn_training %>%
  group_by(currency_code, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_currency

frequency_table_currency

churn_training %>%
  group_by(currency_code, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = currency_code, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(currency_code, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(currency_code, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

## Mailing Code (SIGNIFICANT)

```{r}
churn_training %>%
  group_by(maling_code, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_mailing_code

frequency_table_mailing_code

churn_training %>%
  group_by(maling_code, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = maling_code, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(maling_code, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(maling_code, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

## Paperless Billing (POSSIBLY significant)

```{r}
churn_training %>%
  group_by(paperless_billing, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_paperless

frequency_table_paperless

churn_training %>%
  group_by(paperless_billing, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = paperless_billing, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(paperless_billing, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(paperless_billing, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```
 
## Online Backup
 
```{r}
churn_training %>%
  group_by(online_backup, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_online_backup

frequency_table_online_backup

churn_training %>%
  group_by(online_backup, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = online_backup, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(online_backup, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(online_backup, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

## Payment Method

```{r}
churn_training %>%
  group_by(payment_method, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_payment_method

frequency_table_payment_method

churn_training %>%
  group_by(payment_method, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = payment_method, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(payment_method, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(payment_method, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

```{r}
churn_training %>%
  group_by(gender, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_gender

frequency_table_gender

churn_training %>%
  group_by(gender, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = gender, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(gender, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(gender, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

## Network Speed

```{r}
churn_training %>%
  group_by(network_speed, churn) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = churn, values_from = n, values_fill = 0) %>%
  mutate(n = `0` + `1`,
         pct_churn = round(`1`/n, 3)) %>%
  arrange(desc(pct_churn)) -> frequency_table_network_speed

frequency_table_network_speed

churn_training %>%
  group_by(network_speed, churn) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = network_speed, x = n, fill = churn)) + 
  geom_col()

churn_training %>%
  group_by(network_speed, churn) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(network_speed, pct), x = n, fill = churn)) + 
  geom_col(position = "fill") 
```

## Train/Test Split

```{r}
set.seed(123)

train_test_split <- initial_split(churn_training, prop = 0.7)

train <- training(train_test_split)
test <- testing(train_test_split)
train_cv_folds <- vfold_cv(train, v = 5) 

sprintf("Train PCT: %1.2f%%", nrow(train)/nrow(churn_training) * 100)
sprintf("Test PCT: %1.2f%%", nrow(test)/nrow(churn_training) * 100)
sprintf("Kfold Count: %d", nrow(train_cv_folds))
```

## RF M1 

```{r}
recipe1 <- recipe(churn ~ ., data = train) %>%
  step_rm(ip_address_asn, phone_area_code, email_domain, billing_postal, billing_city, customer_id, billing_address, customer_reg_date, senior_citizen) %>%
  step_impute_median(all_numeric(), -all_outcomes()) %>%
  step_unknown(all_nominal(), -all_outcomes()) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  prep()

rf_model <- rand_forest(
  trees = 100,
  min_n = 10) %>%
  set_engine("ranger",
             importance = "permutation",
             max.depth  = 25) %>% 
  set_mode("classification")
  
#Permutation

rf_workflow <- workflow() %>% 
  add_recipe(recipe1) %>%
  add_model(rf_model)  

rf_fit <- rf_workflow %>%
  fit(data = train)
```

# Evaluate (RF - NOT tuned)

```{r}
#Score (training)  
predict(rf_fit, train, type = "prob") %>%
  bind_cols(predict(rf_fit, train, type = "class")) %>%
  bind_cols(., train) -> scored_train1 

#Score (testing) 
predict(rf_fit, test, type = "prob") %>%
  bind_cols(predict(rf_fit, test, type = "class")) %>%
  bind_cols(., test) -> scored_test1   

#Metrics: Train/Test 
scored_train1 %>% 
  metrics(churn, `.pred_1`, estimate = .pred_class) %>%
  mutate(part = "training") %>%
  bind_rows(scored_test1 %>%
              metrics(churn, `.pred_1`, estimate = .pred_class) %>%
              mutate(part = "testing") ) %>%
  filter(.metric %in% c('accuracy', 'roc_auc')) %>%
  pivot_wider(names_from = .metric, values_from = .estimate)
  
#VIP: top 10
rf_fit %>%
  extract_fit_parsnip() %>%
  vip(num_features = 10)
  
#Confusion Matrices
scored_train1 %>%
  conf_mat(churn, .pred_class) %>%
  autoplot(type = "heatmap")
  
 scored_test1 %>%
  conf_mat(churn, .pred_class) %>%
  autoplot(type = "heatmap")
   
options(yardstick.event_first = FALSE)

#ROC-AUC 
scored_train1 %>%
mutate(model = "train") %>%
bind_rows(scored_test1 %>%
            mutate(model = "test")) %>%
group_by(model) %>%
roc_curve(churn, `.pred_1`) %>%
autoplot() 

#Operating Range 
scored_test1  %>%
roc_curve(churn, `.pred_1`) %>%
mutate(FPR = round((1 - specificity), 2),
       TPR = round(sensitivity, 3),
       score_threshold =  1 - round(.threshold, 3)) %>%
group_by(FPR) %>%
summarise(score_threshold = max(score_threshold),
          TPR = max(TPR)) %>%
  ungroup() %>%
  mutate(precision = TPR/(TPR + FPR)) %>%
  subset(select = c("FPR", "TPR", "precision", "score_threshold")) %>%
  filter(FPR <= 0.2) 

```

## TUNED RF Model (New) ##

```{r, message = FALSE, warning = FALSE}
rf_tuned <- rand_forest(trees = tune(),
                        min_n = tune()) %>%
  set_engine("ranger", importance = "permutation") %>% 
  set_mode("classification")

rf_wf <- workflow() %>% 
  add_recipe(recipe1) %>%
  add_model(rf_tuned)

rf_tune_grid <- grid_random(trees(),
                            min_n(),
                            size = 5)
```

```{r, message = FALSE, warning = FALSE}
all_cores <- detectCores(logical = TRUE)
sprintf("# of Logical Cores: %d", all_cores)
cl <- makeCluster(all_cores)
registerDoParallel(cl)

rf_tuning_results <- rf_wf %>% 
  tune_grid(
    resamples = train_cv_folds,
    grid = rf_tune_grid,
    control = control_resamples(save_pred = TRUE)
    )

rf_tuning_results %>%
  unnest(.notes) ## use this to debug your model
```

```{r, message = FALSE, warning = FALSE}
rf_tuning_results %>%
  collect_metrics()

rf_tuning_results %>%
  show_best("roc_auc") %>%
  print()

rf_best <- rf_tuning_results %>%
  select_best("roc_auc") 

print(rf_best)

rf_final_wf <- rf_wf %>% 
  finalize_workflow(rf_best)

print(rf_final_wf)

rf_final_fit <- rf_final_wf %>%
  fit(data = train)
```

# Evaluate (RF - TUNED)

```{r, message = FALSE, warning = FALSE}
predict(rf_final_fit, train) %>%
  bind_cols(predict(rf_final_fit, train, type = "prob"))%>%
  bind_cols(train) -> train_scored_rf

predict(rf_final_fit, test) %>%
  bind_cols(predict(rf_final_fit, test, type = "prob")) %>%
  bind_cols(test) -> test_scored_rf

print(train_scored_rf,
      test_scored_rf)

precision(train_scored_rf, churn, .pred_class)
recall(test_scored_rf, churn, .pred_class)

train_scored_rf <- model_score(train, rf_final_fit, "rf training")
test_scored_rf <- model_score(test, rf_final_fit, "rf testing")

accuracy_score(train_scored_rf, test_scored_rf)
```

## -- TUNED XGB --

```{r, message = FALSE, warning = FALSE}
xgb_model <- boost_tree(trees = tune(),
                        tree_depth = tune(),
                        min_n = tune(),
                        learn_rate = tune()) %>%
  set_engine("xgboost") %>%
  set_mode("classification")

xgb_workflow <- workflow() %>%
  add_recipe(recipe1) %>%
  add_model(xgb_model)

xgb_tune_grid <- grid_random(trees(),
                             tree_depth(),
                             min_n(),
                             learn_rate(),
                             size = 5)

print(xgb_tune_grid)
```


```{r, message = FALSE, warning = FALSE}
all_cores <- detectCores(logical = TRUE)
sprintf("# of Logical Cores: %d", all_cores)
cl <- makeCluster(all_cores)
registerDoParallel(cl)

xgb_tuning_results <- xgb_workflow %>% 
  tune_grid(
    resamples = train_cv_folds,
    grid = xgb_tune_grid,
    control = control_resamples(save_pred = TRUE)
    )

xgb_tuning_results %>%
  unnest(.notes)
```


```{r, message = FALSE, warning = FALSE}
xgb_tuning_results %>%
  collect_metrics() %>%
  mutate_if(is.numeric, round, 3)

xgb_tuning_results %>%
  show_best("roc_auc") %>%
  print()

xgb_tuning_results %>%
  collect_metrics() %>%
  mutate_if(is.numeric, round,3) %>%
  ggplot(aes(trees, mean, )) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2) 

xgb_tuning_results %>%
  collect_metrics() %>%
  mutate_if(is.numeric, round,3) %>%
  ggplot(aes(tree_depth, mean, )) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2) 

xgb_tuning_results %>%
  collect_metrics()  %>%
  mutate_if(is.numeric, round,3) %>%
  ggplot(aes(min_n, mean, )) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2) 

xgb_best <- xgb_tuning_results %>%
  select_best("roc_auc") 

print(xgb_best)

xgb_final_wf <- xgb_workflow %>% 
  finalize_workflow(xgb_best)

print(xgb_final_wf)

xgb_final_fit <- xgb_final_wf %>%
  fit(data = train)
```

```{r}
predict(xgb_final_fit, train) %>%
  bind_cols(predict(xgb_final_fit, train, type = "prob"))%>%
  bind_cols(train) -> train_scored_rf

predict(xgb_final_fit, test) %>%
  bind_cols(predict(xgb_final_fit, test, type = "prob")) %>%
  bind_cols(test) -> test_scored_rf

print(train_scored_rf,
      test_scored_rf)

precision(train_scored_rf, churn, .pred_class)
recall(test_scored_rf, churn, .pred_class)

train_scored_rf <- model_score(train, xgb_final_fit, "rf training")
test_scored_rf <- model_score(test, xgb_final_fit, "rf testing")

accuracy_score(train_scored_rf, test_scored_rf)
```


#RF M2

```{r}
recipe2 <- 
  recipe(churn ~ ., data = train) %>%
  step_rm(ip_address_asn, phone_area_code, email_domain, billing_postal, billing_city, billing_address, customer_reg_date, senior_citizen, partner, phone_service, multiple_lines, wifi_calling_text, gender, network_speed, online_backup, customer_id) %>% 
  step_impute_median(all_numeric(), -all_outcomes()) %>%
  step_unknown(all_nominal(), -all_outcomes()) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  prep()

rf_model2 <- rand_forest(
  trees = 100,
  min_n = 10) %>%
  set_engine("ranger",
            importance = "permutation",
            max.depth  = 40) %>% 
  set_mode("classification")
  
#Permutation Importance

rf_workflow2 <- workflow() %>% 
  add_recipe(recipe2) %>%
  add_model(rf_model2)  

rf_fit2 <- rf_workflow2 %>%
  fit(data = train)
```

## TUNED RF Model (New) ##

```{r, message = FALSE, warning = FALSE}
rf_tuned2 <- rand_forest(trees = tune(),
                        min_n = tune()) %>%
  set_engine("ranger", importance = "permutation") %>% 
  set_mode("classification")

rf_wf <- workflow() %>% 
  add_recipe(recipe2) %>%
  add_model(rf_tuned2)

rf_tune_grid <- grid_random(trees(),
                            min_n(),
                            size = 5)
```

```{r, message = FALSE, warning = FALSE}
all_cores <- detectCores(logical = TRUE)
sprintf("# of Logical Cores: %d", all_cores)
cl <- makeCluster(all_cores)
registerDoParallel(cl)

rf_tuning_results <- rf_wf %>% 
  tune_grid(
    resamples = train_cv_folds,
    grid = rf_tune_grid,
    control = control_resamples(save_pred = TRUE)
    )

rf_tuning_results %>%
  unnest(.notes) ## use this to debug your model
```

```{r, message = FALSE, warning = FALSE}
rf_tuning_results %>%
  collect_metrics()

rf_tuning_results %>%
  show_best("roc_auc") %>%
  print()

rf_best <- rf_tuning_results %>%
  select_best("roc_auc") 

print(rf_best)

rf_final_wf <- rf_wf %>% 
  finalize_workflow(rf_best)

print(rf_final_wf)

rf_final_fit <- rf_final_wf %>%
  fit(data = train)
```

# Evaluate (RF - TUNED)

```{r, message = FALSE, warning = FALSE}
predict(rf_final_fit, train) %>%
  bind_cols(predict(rf_final_fit, train, type = "prob"))%>%
  bind_cols(train) -> train_scored_rf

predict(rf_final_fit, test) %>%
  bind_cols(predict(rf_final_fit, test, type = "prob")) %>%
  bind_cols(test) -> test_scored_rf

print(train_scored_rf,
      test_scored_rf)

precision(train_scored_rf, churn, .pred_class)
recall(test_scored_rf, churn, .pred_class)

train_scored_rf <- model_score(train, rf_final_fit, "rf training")
test_scored_rf <- model_score(test, rf_final_fit, "rf testing")

accuracy_score(train_scored_rf, test_scored_rf)
```

## Evaluate (RF M2)

```{r}
#Score (training)  
predict(rf_fit2, train, type = "prob") %>%
  bind_cols(predict(rf_fit2, train, type = "class")) %>%
  bind_cols(., train) -> scored_train2 

#Score (testing)
predict(rf_fit2, test, type = "prob") %>%
  bind_cols(predict(rf_fit2, test, type = "class")) %>%
  bind_cols(., test) -> scored_test2   

#Metrics: Train/Test 
scored_train2 %>%
  metrics(churn, `.pred_1`, estimate = .pred_class) %>%
  mutate(part = "training") %>%
  bind_rows(scored_test2 %>%
              metrics(churn, `.pred_1`, estimate = .pred_class) %>%
              mutate(part = "testing") ) %>%
  filter(.metric %in% c('accuracy','roc_auc')) %>%
  pivot_wider(names_from = .metric, values_from = .estimate)
  
#VIP: top 10
rf_fit2 %>%
  extract_fit_parsnip() %>%
  vip(num_features = 10)
  
#Confusion Matrices 
scored_train2 %>%
  conf_mat(churn, .pred_class) %>%
  autoplot(type = "heatmap")
  
scored_test2 %>%
  conf_mat(churn, .pred_class) %>%
  autoplot(type = "heatmap")
   
options(yardstick.event_first = FALSE)
  
#ROC-AUC 
scored_train2 %>%
  mutate(model = "train") %>%
  bind_rows(scored_test2 %>%
              mutate(model = "test")) %>%
  group_by(model) %>%
  roc_curve(churn, `.pred_1`) %>%
  autoplot() 

#Operating Range 
scored_test2  %>%
  roc_curve(churn, `.pred_1`) %>%
  mutate(FPR = round((1 - specificity), 2),
         TPR = round(sensitivity, 3),
         score_threshold = 1 - round(.threshold, 3)) %>%
  group_by(FPR) %>%
  summarise(score_threshold = max(score_threshold),
            TPR = max(TPR))%>%
  ungroup() %>%
  mutate(precision = TPR/(TPR + FPR)) %>%
  subset(select = c("FPR", "TPR", "precision", "score_threshold")) %>%
  filter(FPR <= 0.2)
```

## -- TUNED XGB --

```{r, message = FALSE, warning = FALSE}
xgb_model <- boost_tree(trees = tune(),
                        tree_depth = tune(),
                        min_n = tune(),
                        learn_rate = tune()) %>%
  set_engine("xgboost") %>%
  set_mode("classification")

xgb_workflow <- workflow() %>%
  add_recipe(recipe2) %>%
  add_model(xgb_model)

xgb_tune_grid <- grid_random(trees(),
                             tree_depth(),
                             min_n(),
                             learn_rate(),
                             size = 5)

print(xgb_tune_grid)
```

```{r, message = FALSE, warning = FALSE}
all_cores <- detectCores(logical = TRUE)
sprintf("# of Logical Cores: %d", all_cores)
cl <- makeCluster(all_cores)
registerDoParallel(cl)

xgb_tuning_results <- xgb_workflow %>% 
  tune_grid(
    resamples = train_cv_folds,
    grid = xgb_tune_grid,
    control = control_resamples(save_pred = TRUE)
    )

xgb_tuning_results %>%
  unnest(.notes)
```

```{r, message = FALSE, warning = FALSE}
xgb_tuning_results %>%
  collect_metrics() %>%
  mutate_if(is.numeric, round, 3)

xgb_tuning_results %>%
  show_best("roc_auc") %>%
  print()

xgb_tuning_results %>%
  collect_metrics() %>%
  mutate_if(is.numeric, round,3) %>%
  ggplot(aes(trees, mean, )) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2) 

xgb_tuning_results %>%
  collect_metrics() %>%
  mutate_if(is.numeric, round,3) %>%
  ggplot(aes(tree_depth, mean, )) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2) 

xgb_tuning_results %>%
  collect_metrics()  %>%
  mutate_if(is.numeric, round,3) %>%
  ggplot(aes(min_n, mean, )) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2) 

xgb_best <- xgb_tuning_results %>%
  select_best("roc_auc") 

print(xgb_best)

xgb_final_wf <- xgb_workflow %>% 
  finalize_workflow(xgb_best)

print(xgb_final_wf)

xgb_final_fit <- xgb_final_wf %>%
  fit(data = train)
```

```{r}
predict(xgb_final_fit, train) %>%
  bind_cols(predict(xgb_final_fit, train, type = "prob"))%>%
  bind_cols(train) -> train_scored_rf

predict(xgb_final_fit, test) %>%
  bind_cols(predict(xgb_final_fit, test, type = "prob")) %>%
  bind_cols(test) -> test_scored_rf

print(train_scored_rf,
      test_scored_rf)

precision(train_scored_rf, churn, .pred_class)
recall(test_scored_rf, churn, .pred_class)

train_scored_rf <- model_score(train, xgb_final_fit, "rf training")
test_scored_rf <- model_score(test, xgb_final_fit, "rf testing")

accuracy_score(train_scored_rf, test_scored_rf)
```


## Holdout Preds & Kaggle

```{r, warning=FALSE, message=FALSE}
#Score Training
predict(rf_fit2, churn_holdout, type = "prob") %>%
  bind_cols(predict(rf_fit2, churn_holdout, type = "class")) %>%
  bind_cols(., churn_holdout) -> churn_holdout_score

kaggle <- churn_holdout_score %>%
  mutate(churn = as.factor(if_else(.pred_1 >= 0.10, 1, 0)))

kaggle %>%
  ggplot(aes(.pred_1, fill=churn)) +
  geom_histogram(bins = 100) +
  xlim(0, 1) +
  geom_vline(aes(xintercept = 0.095)) +
  labs(title = "Prediction File Score Distribution")

#Kaggle Submission (CSV)
kaggle <- churn_holdout_score %>%
  mutate(churn = .pred_1) %>%
  subset(select = c("customer_id", "churn"))

kaggle

#write_csv(kaggle, "Project_1_Preds_Tyler_Grosman.csv")
```
