```{r, message=FALSE, warning=FALSE}
library(pROC)
library(caret)
library(tidyverse)
library(lubridate)
library(janitor)
library(skimr)
library(lubridate)
library(RSocrata)
library(tidyquant)
library(tidymodels)
library(ranger)
library(topicmodels)
library(readr)
library(tidyverse)
library(lubridate)
library(dplyr)
library(tidytext)
library(rtweet)
library(readxl)
library(janitor)
library(devtools)
library(Rcpp)
library(vip)
library(ggplot2)
library(corrplot)
library(MASS)
library(VIF)
library(vip)
library(fastDummies)
```

```{r, message=FALSE, warning=FALSE}
lost_sales <- read_csv(file = "LostSales.csv") %>%
  clean_names()
  
```

```{r, message=FALSE, warning=FALSE}
status <- as.factor(lost_sales$status)
part_type <- as.factor(lost_sales$part_type)

skim(lost_sales)

```
# 49.45% of sales do not result in subsequent orders within 30 days.

```{r}
lost_sales %>%
  count(status)

#272/550
```

#   Winning a sale is more likely for AM suppliers. It appears that OE part suppliers have a higher likelihood of losing a sale than do AM suppliers and both pieces of information are evidenced by the graph below. 

```{r, message=FALSE, warning=FALSE}
ggplot(lost_sales, aes(status)) + geom_bar(aes(fill=part_type))

lost_sales %>%
  filter(status == "Lost") %>%
  count(part_type)

```


# likelihood that an order will be lost increases as the quoted price increases; does not appear that quoted price is a significant predictor of losing an order/sale

```{r}
logit_Q1 <- glm(formula = relevel(status, "Lost") ~ lost_sales$quote, family = binomial(link = "logit"))
summary(logit_Q1)
coefficients(logit_Q1)
anova(logit_Q1)
```


```{r, message=FALSE, warning=FALSE}
levels(status)

logit_Q2 <- glm(formula = relevel(status, "Won") ~ lost_sales$time_to_delivery + part_type, family = binomial(link = "logit"))
summary(logit_Q2)
coefficients(logit_Q2)
anova(logit_Q2)

logit_Q3 <- glm(formula = relevel(status, "Won") ~ lost_sales$quote + lost_sales$time_to_delivery + part_type, family = binomial(link = "logit"))
summary(logit_Q3)
coefficients(logit_Q3)
anova(logit_Q3)

step_logit_Q3 <- stepAIC(logit_Q3, direction = "both")
summary(step_logit_Q3)
coefficients(step_logit_Q3)
anova(step_logit_Q3)
plot(step_logit_Q3)
```

```{r, message=FALSE, warning=FALSE}
pvalue <- predict(step_logit_Q3, lost_sales, type = "response")
pstatus <- ifelse(pvalue >0.5, "Lost", "Won")
pstatus <- as.factor(pstatus)
lost_sales_status <- pstatus
lost_sales_probability <- pvalue
p_status <- as.factor(lost_sales_status)
```

# model appears to be somewhat useful for predicting likelihood of lost sale (balanced accuracy rate = 0.5971); misclassification rate= 0.4029 (1-0.5971); ROC-AUC= 0.6376

#  model appears to be better at predicting sales won rather than sales lost and should be noted that it can still give us insight into lost sales as long as we are working with probablities between 0-1; can subtract probability of winning a sale from 1 to generate probablity lost sale

```{r, message=FALSE, warning=FALSE}
confusionMatrix(p_status, status)
roc(status, pvalue, plot = TRUE, auc = TRUE)
```

#Actions that could be taken to prevent the sale from being lost or to similarly increase the likelihood that the sale is won:
  #- would be expediting manufacturing/shipping processes of individual part or alternatively giving discount to purchasing party 

```{r}
lost_sales %>%
  summarize(mean(quote))
#-7.768e-01+1.931e-05*(1400)+1.837e-02*(20)+4.711e-01*(0)
```

# Misclassfication rates decrease across the models as insignificant variables are removed. If the final model can more accurately predict loss/won status then it means we are analyzing statistically significant predictors (even if they may not be the most relevant predictors for our particular analysis) so this should be expected. The best model that we created was the reduced or partial model with a misclassification rate of about 40.3%. The model could potentially be improved by including other variables such as the vehicle type (in order to understand if sales are being lost in a particular sector of the automotive industry). Part type gives us some information about this, however it only refers to the production type of the part itself and does not reference vehicle type in any way. Additionally, 

