```{r, message=FALSE, warning=FALSE}
library(pROC)
library(caret)
library(tidyverse)
library(lubridate)
library(janitor)
library(skimr)
library(lubridate)
library(RSocrata)
library(tidyquant)
library(tidymodels)
library(ranger)
library(topicmodels)
library(readr)
library(tidyverse)
library(lubridate)
library(dplyr)
library(tidytext)
library(rtweet)
library(readxl)
library(janitor)
library(devtools)
library(Rcpp)
library(vip)
library(ggplot2)
library(corrplot)
library(MASS)
library(VIF)
library(vip)
library(fastDummies)
library(kableExtra)
library(GGally)
library(kableExtra)
library(fastshap)
library(rpart.plot)
```


```{r}
organics <- read_csv("organics.csv") %>%
  clean_names() %>%
  mutate(target_buy = as.factor(target_buy))

new_organics <- read_csv("New_organics.csv") %>%
  clean_names()
```

```{r}
skim(organics)

organics %>%
  count(dem_gender) %>%
  arrange(desc(n))
organics %>%
  count(dem_affl) %>%
  arrange(desc(n))
organics %>%
  count(dem_cluster_group) %>%
  arrange(desc(n))
organics %>%
  count(dem_reg) %>%
  arrange(desc(n))
organics %>%
  count(dem_tv_reg) %>%
  arrange(desc(n))
organics %>%
  count(prom_class) %>%
  arrange(desc(n))
```

```{r}
char_explore <- function(col) {
   organics %>%
     ggplot(., aes(!!as.name(col))) +
     geom_bar(aes(fill = target_buy), position = "fill")
}

organics %>%
  ggplot(aes(x = target_buy)) +
  geom_histogram(stat = "count") +
  labs(title = "Customers Who Purchased Organic: 'No' = 0 vs. 'Yes' = 1")

organics %>%
  group_by(target_buy) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(pct = n/sum(n))

```

```{r}
organics %>%
  ggplot(aes(target_buy)) + 
  geom_histogram(data = subset(organics, target_buy == '1'), fill = "red", alpha = 0.2, stat = "count", bins = 3) +
  geom_histogram(data = subset(organics, target_buy == '0'), fill = "blue", alpha = 0.2, stat = "count", bins = 3) +
  theme(axis.text.x = element_text(angle = 1, hjust = 1)) +
  labs(title = "", x = "", y = "")
```


```{r}
options(scipen = 10)

ggplot(organics, aes(target_buy)) + geom_bar(aes(fill=dem_cluster_group))

organics %>%
  count(dem_cluster_group)

ggplot(organics, aes(x = dem_affl)) +
  geom_histogram(data = subset(organics, target_buy == '1'), fill = "red", alpha = 0.2, bins = 35) +
  geom_histogram(data = subset(organics, target_buy == '0'), fill = "blue", alpha = 0.2, bins = 35) +
  labs(title = "target_buy by dem_affl ('Yes' = red, 'No' = blue)")

ggplot(organics, aes(x = dem_age)) +
  geom_histogram(data = subset(organics, target_buy == '1'), fill = "red", alpha = 0.2) +
  geom_histogram(data = subset(organics, target_buy == '0'), fill = "blue", alpha = 0.2) +
  labs(title = "target_buy by dem_age ('Yes' = red, 'No' = blue)")

ggplot(organics, aes(x = dem_cluster_group)) +
  geom_histogram(data = subset(organics, target_buy == '1'), fill = "red", alpha = 0.2, stat = "count", bins = 8) +
  geom_histogram(data = subset(organics, target_buy == '0'), fill = "blue", alpha = 0.2, stat = "count", bins = 8) +
  labs(title = "target_buy by dem_cluster_group ('Yes' = red, 'No' = blue)")

ggplot(organics, aes(x = dem_gender)) +
  geom_histogram(data = subset(organics, target_buy == '1'), fill = "red", alpha = 0.2, stat = "count", bins = 3) +
  geom_histogram(data = subset(organics, target_buy == '0'), fill = "blue", alpha = 0.2, stat = "count", bins = 3) +
  labs(title = "target_buy by dem_gender ('Yes' = red, 'No' = blue)")

ggplot(organics, aes(x = dem_reg)) +
  geom_histogram(data = subset(organics, target_buy == '1'), fill = "red", alpha = 0.2, stat = "count", bins = 6) +
  geom_histogram(data = subset(organics, target_buy == '0'), fill = "blue", alpha = 0.2, stat = "count", bins = 6) +
  labs(title = "target_buy by dem_reg ('Yes' = red, 'No' = blue)")

ggplot(organics, aes(x = dem_tv_reg)) +
  geom_histogram(data = subset(organics, target_buy == '1'), fill = "red", alpha = 0.2, stat = "count", bins = 14) +
  geom_histogram(data = subset(organics, target_buy == '0'), fill = "blue", alpha = 0.2, stat = "count", bins = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "target_buy by dem_tv_reg ('Yes' = red, 'No' = blue)")

ggplot(organics, aes(x = prom_class)) +
  geom_histogram(data = subset(organics, target_buy == '1'), fill = "red", alpha = 0.2, stat = "count", bins = 3) +
  geom_histogram(data = subset(organics, target_buy == '0'), fill = "blue", alpha = 0.2, stat = "count", bins = 3) +
  labs(title = "target_buy by prom_class ('Yes' = red, 'No' = blue)")

ggplot(organics, aes(x = prom_spend)) +
  geom_histogram(data = subset(organics, target_buy == '1'), fill = "red", alpha = 0.2) +
  geom_histogram(data = subset(organics, target_buy == '0'), fill = "blue", alpha = 0.2) +
  labs(title = "Target_buy by prom_spend ('Yes' = red, 'No' = blue)")

ggplot(organics, aes(x = prom_time)) +
  geom_histogram(data = subset(organics, target_buy == '1'), fill = "red", alpha = 0.2, bins = 3) +
  geom_histogram(data = subset(organics, target_buy == '0'), fill = "blue", alpha = 0.2, bins = 3) +
  labs(title = "Target_buy by prom_time ('Yes' = red, 'No' = blue)")

```


```{r}
organics_prep <- organics %>%
  mutate_if(is.character, factor) %>%
  mutate(target_amt = as.factor(target_amt))
head(organics_prep)

```

```{r}
set.seed(50)

organics_split <- initial_split(organics_prep, prop = 0.7)

organics_train <- training(organics_split)

organics_test <- testing(organics_split)

sprintf("Training Percentage: %1.2f%%", nrow(organics_train)/nrow(organics) * 100)
sprintf("Testing Percentage: %1.2f%%", nrow(organics_test)/nrow(organics) * 100)

head(organics_train)
```

```{r}
organics_recipe <- recipe(target_buy ~ ., data = organics_train) %>%
  step_rm(id, dem_cluster, target_amt) %>%
  step_naomit(all_nominal(), all_numeric(), -all_outcomes()) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  prep()
organics_recipe
```

```{r}
bake_train <- bake(organics_recipe, new_data = organics_train)
bake_test <- bake(organics_recipe, new_data = organics_test)
```

```{r}
logistic_model <- logistic_reg(mode = "classification") %>%
  set_engine("glm") %>%
  fit(target_buy ~ ., data = bake_train)

tidy(logistic_model) %>%
  mutate_at(c("estimate", "std.error", "statistic", "p.value"), round, 10)
```

```{r}
predict(logistic_model, bake_train, type = "prob") %>%
  bind_cols(., predict(logistic_model, bake_train)) %>%
  bind_cols(., bake_train) -> scored_train_model
head(scored_train_model)

predict(logistic_model, bake_test, type = "prob") %>%
  bind_cols(., predict(logistic_model, bake_test)) %>%
  bind_cols(., bake_test) -> scored_test_model
head(scored_test_model)
```

```{r}
options(yardstick.event_first = FALSE)

scored_test_model %>%
  metrics(target_buy, .pred_1, estimate = .pred_class) %>%
  mutate(part = "testing") %>%
  bind_rows(scored_train_model %>%
              metrics(target_buy, .pred_1, estimate = .pred_class) %>%
              mutate(part = "training")) %>%
  filter(.metric == "roc_auc")

logistic_model %>%
  vip(num_features = 5)

scored_train_model %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_model %>%
              mutate(model = "test")) %>%
  group_by(model) %>%
  roc_curve(target_buy, .pred_1) %>%
  autoplot()

scored_train_model %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title = "Training Confusion Matrix")

scored_test_model %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title = "Testing Confusion Matrix")

scored_train_model %>%
  ggplot() +
  geom_density(aes(x = .pred_1, fill = target_buy), alpha = 0.5) +
  labs(title = "Distribution of Training Scores")

scored_test_model %>%
  ggplot() +
  geom_density(aes(x = .pred_1, fill = target_buy), alpha = 0.5) +
  labs(title = "Distribution of Testing Scores")
```

```{r}
step_log <- glm(target_buy ~ ., data = bake_train, family = binomial(link = "logit"))
step_model <- stepAIC(step_log, direction = "both")
summary(step_log)
summary(step_model)
```

```{r}
step_recipe <- recipe(target_buy ~ dem_affl + dem_age + dem_cluster_group + dem_gender + dem_reg + prom_class, data = organics_train) %>%
  step_impute_mode(all_nominal(), -all_outcomes()) %>%
  step_impute_median(all_numeric()) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  prep()
step_recipe
```

```{r}
bake_step_train <- bake(step_recipe, new_data = organics_train)
bake_step_test <- bake(step_recipe, new_data = organics_test)
```

```{r}
logistic_step_model <- logistic_reg(mode = "classification") %>%
  set_engine("glm") %>%
  fit(target_buy ~ ., data = bake_step_train)

tidy(logistic_step_model) %>%
  mutate_at(c("estimate", "std.error", "statistic", "p.value"), round, 10)
```

```{r}
predict(logistic_step_model, bake_step_train, type = "prob") %>%
  bind_cols(., predict(logistic_step_model, bake_step_train)) %>%
  bind_cols(., bake_step_train) -> scored_train_step
head(scored_train_step)

predict(logistic_step_model, bake_step_test, type = "prob") %>%
  bind_cols(., predict(logistic_step_model, bake_step_test)) %>%
  bind_cols(., bake_step_test) -> scored_test_step
head(scored_test_step)
```

```{r}
scored_train_step %>%
  metrics(target_buy, .pred_1, estimate = .pred_class) %>%
  mutate(part = "training") %>%
  bind_rows(scored_test_step %>%
              metrics(target_buy, .pred_1, estimate = .pred_class) %>%
              mutate(part = "testing")) %>%
  filter(.metric == "roc_auc")

logistic_step_model %>%
  vip(num_features = 10)

scored_train_step %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_step %>%
              mutate(model = "test")) %>%
  group_by(model) %>%
  roc_curve(target_buy, .pred_1) %>%
  autoplot()

scored_train_step %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title = "Confusion Matrix - Training (Step)")

scored_test_step %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title = "Confusion Matrix - Testing (Step)")
```

```{r}
tree_model <- decision_tree(mode="classification") %>%
                  set_engine("rpart") %>%
                  fit(target_buy ~ ., data = bake_train)
tree_model$fit

options(scipen=0)
rpart.plot(tree_model$fit, roundint=FALSE, extra = 3)
```

```{r}
tree_model_2 <- decision_tree(mode="classification",
                            cost_complexity = 0.001,
                            tree_depth = 5,
                            min_n = 2) %>%
                  set_engine("rpart") %>%
                  fit(target_buy ~ ., data = bake_train)

tree_model_2$fit

options(scipen = 0)

rpart.plot(tree_model_2$fit, roundint = FALSE, extra = 3)
```

```{r}
predict(tree_model, bake_train, type = "prob") %>%
  bind_cols(.,predict(tree_model, bake_train)) %>%
  bind_cols(.,bake_train) -> scored_train_tree

head(scored_train_tree)

predict(tree_model, bake_test, type = "prob") %>%
  bind_cols(.,predict(tree_model, bake_test)) %>%
  bind_cols(.,bake_test) -> scored_test_tree

head(scored_test_tree)
```

```{r}
options(yardstick.event_first = FALSE)

scored_train_tree %>% 
  metrics(target_buy, .pred_1, estimate = .pred_class) %>%
  mutate(part="training") %>%
  bind_rows(scored_test_tree %>% 
               metrics(target_buy, .pred_1, estimate = .pred_class) %>%
               mutate(part="testing")) 
  
tree_model %>%
  vip(num_features = 5)

scored_train_tree %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_tree %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(target_buy, .pred_1) %>%
  autoplot()

scored_train_tree %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Confusion Matrix (Train)")

scored_test_tree %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Confusion Matrix (Test)")
```

```{r}
predict(tree_model_2, bake_train, type = "prob") %>%
  bind_cols(.,predict(tree_model_2, bake_train)) %>%
  bind_cols(.,bake_train) -> scored_train_tree_2

head(scored_train_tree_2)

predict(tree_model_2, bake_test, type = "prob") %>%
  bind_cols(.,predict(tree_model_2, bake_test)) %>%
  bind_cols(.,bake_test) -> scored_test_tree_2

head(scored_test_tree_2)
```

```{r}
scored_train_tree_2 %>% 
  metrics(target_buy, .pred_1, estimate = .pred_class) %>%
  mutate(part="training") %>%
  bind_rows(scored_test_tree_2 %>% 
               metrics(target_buy, .pred_1, estimate = .pred_class) %>%
               mutate(part="testing")) %>%
  filter(.metric == "accuracy")

tree_model_2 %>%
  vip(num_features = 5)

scored_train_tree_2 %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_tree_2 %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(target_buy, .pred_1) %>%
  autoplot()

scored_train_tree_2 %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Confusion Matrix (Train)")

scored_test_tree_2 %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Confusion Matrix (Test)")
```

#NEW_ORGANICS.CSV

```{r}
new_organics_prep <- new_organics %>%
  clean_names()
head(new_organics_prep)

```

```{r}
skim(new_organics_prep)

new_organics_prep %>%
  count(dem_gender) %>%
  arrange(desc(n))
new_organics_prep %>%
  count(dem_affl) %>%
  arrange(desc(n))
new_organics_prep %>%
  count(dem_cluster_group) %>%
  arrange(desc(n))
new_organics_prep %>%
  count(dem_reg) %>%
  arrange(desc(n))
new_organics_prep %>%
  count(dem_tv_reg) %>%
  arrange(desc(n))
new_organics_prep %>%
  count(prom_class) %>%
  arrange(desc(n))
```

```{r}
bake_new <- bake(organics_recipe, new_data = new_organics_prep)

bake_new_2 <- bake(step_recipe, new_data = bake_new)
```


```{r}
predict(tree_model_2, bake_new, type = "prob") %>%
  bind_cols(.,predict(tree_model_2, bake_new)) %>%
  bind_cols(.,bake_new) -> scored_new_organics

head(scored_new_organics)
```

```{r}
write_xlsx(scored_new_organics, 'C:\\Users\\tyler\\Documents\\Scored_New_Organics.xlsx')
```





Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
