
```{r}
library(ggplot2)
library(corrplot)
library(MASS)
library(skimr)
library(readr)
library(VIF)
library(fastDummies)
```

```{r}
data_car <- read_csv("bluebookregression.csv")
data_car1 <- subset(data_car, select = c(Price, Cylinder, Liter, Doors, Cruise, Sound, Leather, Mileage))
data_car1
```

```{r}
data_car1 %>%
  ggplot(aes(x=Price, y=Mileage))+
  geom_point() +
  labs(title = "PRICE vs. MILEAGE", 
       x = "Price", y = "Mileage")
```

```{r}
cor(data_car$Price, data_car$Mileage)
```

```{r}
simple_model <- lm(Price ~ Mileage, data = data_car)
simple_model
summary(simple_model)
```

```{r}
cormat <- cor(data_car1)
round(cormat, 2)
corrplot(cormat)
pairs(data_car1[2:5])
```

```{r}
fullreg <- lm(Price~., data_car1)
fullreg
summary(fullreg)
```

```{r}
reg1 <- lm(Price ~ Cylinder + Liter + Cruise, data_car1)
reg1
summary(reg1)
```

```{r}
reg2 <- lm(Price ~ Cylinder + Doors + Cruise + Sound + Leather + Mileage, data_car1)
reg2
summary(reg2)
```

```{r}
reg3<- lm(Price ~ Cylinder + Doors + Cruise + Sound + Leather, data_car1)
reg3
summary(reg3)
```

```{r}
step <- stepAIC(fullreg, direction="both")
summary(step)
```

```{r}
#looks at spread of residuals as mileage changes
data_car1 %>%
  ggplot(aes(x=Mileage, y=residuals(step)))+
  geom_point() +
  labs(x = "Mileage", y = "Residuals")

#looks at the spread of the residuals as the predicted price changes
data_car1 %>%
  ggplot(aes(x=fitted(step), y=residuals(step)))+
  geom_point() +
  labs(title = "RESIDUALS VS FITTED", 
       x = "Residuals", y = "Fitted")

#looks at histogram of residuals
data_car1 %>%
  ggplot(aes(x=residuals(step)))+
  geom_histogram() +
  labs(x = "Residuals(step)", y = "Count")

plot(step)
```

```{r}
reg4<- lm(log10(Price) ~ Cylinder + Doors + Cruise + Sound + Leather + Mileage, data_car1)
reg4
summary(reg4)
plot(reg4)
```

```{r}
reg5<- lm(sqrt(Price) ~ Cylinder + Doors + Cruise + Sound + Leather + Mileage, data_car1)
reg5
summary(reg5)
plot(reg5)
```

```{r}
plot(step)
```

```{r}

Q1 <- quantile(data_car1$Price, .25)
Q3 <- quantile(data_car1$Price, .75)
IQR <- IQR(data_car1$Price)

#only keep rows in dataframe that have values within 1.5*IQR of Q1 and Q3
no_outliers <- subset(data_car1, data_car1$Price > (Q1 - 1.5*IQR) & data_car1$Price < (Q3 + 1.5*IQR))
head(no_outliers)
```


```{r}
reg6<- lm(Price ~ Cylinder + Doors + Cruise + Sound + Leather + Mileage, no_outliers)
reg6
summary(reg6)
plot(reg6)
```

```{r}
reg7<- lm(log10(Price) ~ Cylinder + Doors + Cruise + Sound + Leather + Mileage, no_outliers)
reg7
summary(reg7)
plot(reg7)
```

#Regression 1 removes all variables & keeps mileage while using the dataset including outliers
#Regression 2 keeps all variables & uses dataset including outliers
#Regression 3 keeps all variables & uses dataset which has removed outliers
#Regression 4 removes all variables except for mileage & uses dataset which has removed outliers

```{r}
#looks at histogram of residuals for original regression
data_car1 %>%
  ggplot(aes(x=residuals(step)))+
  geom_histogram() +
  labs(x = "Residuals(step)", y = "Count")

#remove all explanatory variables except mileage
reg8<- lm(log10(Price) ~ Mileage, data_car1)

#multivariable regression w/ natural log
reg9<- lm(log10(Price) ~ Cylinder + Doors + Cruise + Sound + Leather + Mileage, data_car1)

#multivariable regression using natural log and removing outliers
reg10<- lm(log10(Price) ~ Cylinder + Doors + Cruise + Sound + Leather + Mileage, no_outliers)

#remove all explanatory variables except mileage and remove outliers
reg11<- lm(log10(Price) ~ Mileage, no_outliers)

data_car1 %>%
  ggplot(aes(x=residuals(reg8)))+
  geom_histogram() +
  labs(x = "Residuals(reg8)", y = "Count")

data_car1 %>%
  ggplot(aes(x=residuals(reg9)))+
  geom_histogram() +
  labs(x = "Residuals(reg9)", y = "Count")

no_outliers %>%
  ggplot(aes(x=residuals(reg10)))+
  geom_histogram() +
  labs(x = "Residuals(reg10)", y = "Count")

no_outliers %>%
  ggplot(aes(x=residuals(reg11)))+
  geom_histogram() +
  labs(x = "Residuals(reg11)", y = "Count")
```

#Multicollinearity
```{r}
reg12<- lm(Price ~ Mileage + Liter, data_car1)
reg13<- lm(Price ~ Mileage + Cylinder, data_car1)
reg14<- lm(Price ~ Mileage + Liter + Cylinder, data_car1)
summary(reg12)
summary(reg13)
summary(reg14)
```

```{r}
#look at the correlation between Liter and Cylinder variables
cor(data_car1$Liter, data_car1$Cylinder)
```

```{r}
data_car2 <- subset(data_car, select = c(Make, Model, Trim, Type, Price, Liter, Doors, Cruise, Sound, Leather, Mileage))
#This step will turn the specified columns into dummy variables and then remove the cumulative columns 
dataf <- dummy_cols(data_car2, select_columns = c('Make', 'Model','Trim','Type'), remove_selected_columns =TRUE)
head(dataf)
```

```{r}
boxplot(Price~Make, data = data_car2, main = "Price vs. Make", xlab = "Make", ylab = "Price")
boxplot(Price~Model, data = data_car2, main = "Price vs. Model", xlab = "Model", ylab = "Price")
boxplot(Price~Trim, data = data_car2, main = "Price vs. Trim", xlab = "Trim", ylab = "Price")
boxplot(Price~Type, data = data_car2, main = "Price vs. Type", xlab = "Type", ylab = "Price")
```


## Regression model with dummy variables

```{r}
reg15<- lm(Price ~ ., data =  dataf)
summary(reg15)
plot(reg15)
```

```{r}
reg16 <- lm(Price ~ Mileage + Make_Buick + Make_Cadillac + Make_Chevrolet + Make_Pontiac + Make_SAAB + Make_Saturn, data = dataf)
summary(reg16)
plot(reg16)
```

##Interaction Term Models
```{r}
reg17 <- lm(Price~ Mileage + Cylinder, data = data_car1)
summary(reg17)
```

## Regression looking at the interaction between mileage and cylinder

```{r}
reg18 <- lm(Price ~ Mileage*Cylinder, data = data_car1)
summary(reg18)
plot(reg18)
```

```{r}
predict(reg17, data.frame(Mileage = 10000, Cylinder = 4))
predict(reg17, data.frame(Mileage = 10000, Cylinder = 8))
predict(reg18, data.frame(Mileage = 10000, Cylinder = 4))
predict(reg18, data.frame(Mileage = 10000, Cylinder = 8))
```

## Predict when Mileage = 11,000
```{r}
predict(reg17, data.frame(Mileage = 11000, Cylinder = 4))
predict(reg17, data.frame(Mileage = 11000, Cylinder = 8))
predict(reg18, data.frame(Mileage = 11000, Cylinder = 4))
predict(reg18, data.frame(Mileage = 11000, Cylinder = 8))
```

```{r}
reg19 <- lm(Price~ Mileage, data = data_car1)
summary(reg19)
plot(reg19)
```

```{r}
reg20 <- lm(Price~ Mileage*Mileage, data = data_car1)
summary(reg20)
plot(reg20)
````






