```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(pROC)
library(caret)
library(tidyverse)
library(lubridate)
library(janitor)
library(skimr)
library(lubridate)
library(RSocrata)
library(tidyquant)
library(tidymodels)
library(ranger)
library(topicmodels)
library(readr)
library(tidyverse)
library(lubridate)
library(dplyr)
library(tidytext)
library(rtweet)
library(readxl)
library(janitor)
library(devtools)
library(Rcpp)
library(vip)
library(ggplot2)
library(ggthemes)
library(corrplot)
library(corrr)
library(MASS)
library(VIF)
library(vip)
library(fastDummies)
library(kableExtra)
library(GGally)
library(kableExtra)
library(parallel)
library(doParallel)
library(fastshap)
library(rpart.plot)
library(ggpubr)
library(imputeTS)
library(xgboost)
library(glmnet)     #lasso and regularization 
library(rpart.plot) #plotting decision trees 
library(reshape2)
```

```{r}
fraud_original <- read_csv("project_2_training.csv", show_col_types = FALSE) %>%
  clean_names() %>%
  mutate(event_label = as_factor(event_label))

fraud_training <- read_csv("project_2_training.csv", show_col_types = FALSE) %>%
  clean_names() %>%
  mutate(user_agent = str_sub(user_agent, 1, 11)) %>%
  mutate(event_timestamp = as.Date.character(event_timestamp, format = "%Y-%m-%d")) %>%
  mutate(event_label = as_factor(event_label)) %>%
  mutate(billing_postal = round(as.numeric(billing_postal))) %>%
  mutate(card_bin = round(as.numeric(card_bin))) %>%
  mutate_if(is.character, as_factor)
fraud_training %>%
  head()

email_domain_fraud_rate <- fraud_training %>%
  group_by(event_label, email_domain) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0.0) %>%
  mutate(email_domain_pct_fraud = fraud/(fraud + legit)) %>%
  dplyr::select(email_domain, email_domain_pct_fraud)

email_domain_fraud_rate

billing_postal_fraud_rate <- fraud_training %>%
  group_by(event_label, billing_postal) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0.0) %>%
  mutate(billing_postal_pct_fraud = fraud/(fraud + legit)) %>%
  dplyr::select(billing_postal, billing_postal_pct_fraud)

billing_postal_fraud_rate

cvv_fraud_rate <- fraud_training %>%
  group_by(event_label, cvv) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0.0) %>%
  mutate(cvv_pct_fraud = fraud/(fraud + legit)) %>%
  dplyr::select(cvv, cvv_pct_fraud)
cvv_fraud_rate

signature_image_fraud_rate <- fraud_training %>%
  group_by(event_label, signature_image) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0.0) %>%
  mutate(signature_pct_fraud = fraud/(fraud + legit)) %>%
  dplyr::select(signature_image, signature_pct_fraud)

transaction_type_fraud_rate <- fraud_training %>%
  group_by(event_label, transaction_type) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0.0) %>%
  mutate(transaction_type_pct_fraud = fraud/(fraud + legit)) %>%
  dplyr::select(transaction_type, transaction_type_pct_fraud)
transaction_type_fraud_rate

transaction_env_fraud_rate <- fraud_training %>%
  group_by(event_label, transaction_env) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0.0) %>%
  mutate(transaction_env_pct_fraud = fraud/(fraud + legit)) %>%
  dplyr::select(transaction_env, transaction_env_pct_fraud)
transaction_env_fraud_rate

transaction_initiate_fraud_rate <- fraud_training %>%
  group_by(event_label, tranaction_initiate) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0.0) %>%
  mutate(transaction_initiate_pct_fraud = fraud/(fraud + legit)) %>%
  dplyr::select(tranaction_initiate, transaction_initiate_pct_fraud)
transaction_initiate_fraud_rate

fraud_comparison <- fraud_training %>%
  left_join(email_domain_fraud_rate) %>%
  subset(select = -email_domain) %>%
  left_join(billing_postal_fraud_rate) %>%
  subset(select = -billing_postal) %>%
  left_join(cvv_fraud_rate) %>%
  subset(select = -cvv) %>%
  left_join(signature_image_fraud_rate) %>%
  subset(select = -signature_image) %>%
  left_join(transaction_type_fraud_rate) %>%
  subset(select = -transaction_type) %>%
  left_join(transaction_env_fraud_rate) %>%
  subset(select = -transaction_env) %>%
  left_join(transaction_initiate_fraud_rate) %>%
  subset(select = -tranaction_initiate)
  
fraud_comparison

fraud_holdout <- read_csv("holdout.csv") %>%
  clean_names() %>%
  mutate(user_agent = str_sub(user_agent, 1, 11)) %>%
  mutate(event_timestamp = as.Date.character(event_timestamp, format = "%Y-%m-%d")) %>%
  mutate(billing_postal = round(as.numeric(billing_postal))) %>%
  mutate(card_bin = round(as.numeric(card_bin))) %>%
  mutate_if(is.character, as_factor) %>%
  left_join(email_domain_fraud_rate) %>%
  subset(select = -email_domain) %>%
  left_join(billing_postal_fraud_rate) %>%
  subset(select = -billing_postal) %>%
  left_join(cvv_fraud_rate) %>%
  subset(select = -cvv) %>%
  left_join(signature_image_fraud_rate) %>%
  subset(select = -signature_image) %>%
  left_join(transaction_type_fraud_rate) %>%
  subset(select = -transaction_type) %>%
  left_join(transaction_env_fraud_rate) %>%
  subset(select = -transaction_env) %>%
  left_join(transaction_initiate_fraud_rate) %>%
  subset(select = -tranaction_initiate)
fraud_holdout %>%
  head()

holdout_raw <- read_csv("holdout.csv") %>% subset(select = -score)
```

```{r}
skim_without_charts(fraud_original)
skim_without_charts(fraud_training)
skim_without_charts(fraud_holdout)
```

## Target Exploration 

```{r}
fraud_original %>%
  group_by(event_label) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) -> fraud_rate

fraud_rate

training_plot <- ggtexttable(fraud_rate, rows = NULL, 
                        theme = ttheme("mOrange"))

fraud_rate %>%
  ggplot(aes(x = event_label, y = n)) +
  geom_col() + labs("Fraud Rate") -> p1

fraud_rate %>%
  ggplot(aes(x = event_label, y = pct)) +
  geom_col() + labs(title = "Fraud Rate") -> p2

ggarrange(p2, training_plot, 
          ncol = 1, nrow = 2,
          heights = c(1, 0.3))
```

```{r}
fraud_cormat <- fraud_original %>%
  mutate(event_label = as.numeric(event_label)) %>%
  select_if(is.numeric) %>%
  na.omit() %>%
  cor() %>%
  round(digits = 4) %>%
  melt()

fraud_cormat %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(mid = "#FBFEF9",low = "#A63446",high = "#0C6291") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_text(aes(label = round(value, 3)), color = "blue") +
  labs(title = "Correlation Matrix")
```

## -- Numerical Variable Exploration -- 
## (account_age_days, transaction_amt, transaction_adj_amt, historic_velocity, billing_postal, card_bin, days_since_last_logon, inital_amount)

```{r}
nrows <- nrow(fraud_original)
sprintf("rice rule bins = %d",floor((nrows^(1/3))*2))

plot_num <- function(variable, variable_name){
  fraud_original %>%
    ggplot(aes(x = variable)) +
    geom_histogram(aes(y = ..density.., fill = event_label), position = "fill", bins = 100) + 
    stat_function(fun = dnorm, colour = "blue", 
                args = list(mean = mean(variable), 
                            sd = sd(variable))) +
  labs(title = paste("Histogram of", variable_name, sep = " "), x = variable_name, y = "percent")
}

fraud_original %>%
  ggplot(aes(card_bin, fill = event_label)) +
  geom_histogram(stat = "count")
plot_num(fraud_original$account_age_days,"account_age_days")
plot_num(fraud_original$transaction_amt,"transaction_amt")
plot_num(fraud_original$transaction_adj_amt,"transaction_adj_amt")
plot_num(fraud_original$historic_velocity,"historic_velocity")
plot_num(fraud_original$days_since_last_logon,"days_since_last_logon")
plot_num(fraud_original$inital_amount,"initial_amount")
```

```{r}
fraud_num <- fraud_original %>%
  dplyr::select(-event_id, event_timestamp)
         
numeric_graphs <- function(col){
  ggplot(fraud_num,aes(y=event_label,x=!!as.name(col)))+
    geom_boxplot() +
    labs(title = paste("Fraud vs ",col,sep = ""))
}

for (column in names(fraud_num %>% select_if (is.numeric))){
    chart <- numeric_graphs(column)
    print(chart)
  }
```

## Categorical variables

```{r}
fraud_factor <- fraud_original %>%
  subset(select = c("user_agent", "email_domain", "event_label", "billing_state", "currency", "cvv", "signature_image", "transaction_type", "transaction_env", "tranaction_initiate"))

fraud_char <- function(col) {
    ggplot(fraud_factor, aes(x=!!as.name(col))) + 
    geom_bar(aes(fill = event_label), position = "fill") +
    geom_hline(yintercept=0.05428)+
    labs(title = paste("Fraud vs ", col, sep = ""), x = col, y = "Percent Fraud")
}

for (col in names(fraud_factor %>% select_if(is.factor))){
  if (col != 'event_label'){
    chart1 <- fraud_char(col)
    print(chart1)
  }
}
```

```{r}
email_domain_fr <- fraud_original %>%
  group_by(event_label, email_domain) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0.0) %>%
  mutate(email_domain_pct_fraud = fraud/(fraud + legit)) %>%
  dplyr::select(email_domain, email_domain_pct_fraud)

email_domain_fr

fraud_comparison <- fraud_original %>%
  left_join(email_domain_fraud_rate) %>%
  subset(select = -email_domain)

billing_postal_fr <- fraud_original %>%
  group_by(event_label, billing_postal) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0.0) %>%
  mutate(billing_postal_pct_fraud = fraud/(fraud + legit)) %>%
  dplyr::select(billing_postal, billing_postal_pct_fraud)

billing_postal_fr

```

```{r}
options(scipen = 10)

fraud_original %>%
  mutate(event_label = as.character(event_label)) %>%
  ggplot(aes(x = inital_amount, fill = event_label)) +
  geom_bar() +
  labs(title = "initial amount & fraud") +
  ylab("") +
  xlab("initial ammount")

fraud_original %>%
  mutate(event_label = as.character(event_label)) %>%
  ggplot(aes(y = transaction_amt, x = event_label, fill = event_label)) +
  geom_boxplot() +
  labs(title = "Transaction Amounts And Fraud") +
  ylab("transaction_amt") +
  xlab("event_label")

fraud_original %>%
  mutate(event_label = as.character(event_label)) %>%
  ggplot(aes(transaction_adj_amt, fill = event_label)) +
  geom_histogram(bins = 25, position = "fill") +
  labs(title = "") +
  ylab("pct") +
  xlab("")

fraud_original %>%
  mutate(event_label = as.character(event_label)) %>%
  ggplot(aes(historic_velocity, fill = event_label)) +
  geom_histogram(stat = "count", bins = 50, position = "fill") +
  labs(title = " & ") +
  ylab("Count") +
  xlab("")

fraud_original %>%
  mutate(event_label = as.character(event_label)) %>%
  ggplot(aes(days_since_last_logon, fill = event_label)) +
  geom_histogram(bins = 50, postion = "fill") +
  labs(title = "days_since_last_logon & fraud") +
  ylab("Number of Days Since Last Logon") +
  xlab("Fraud")
```

## Scatterplots

```{r}
fraud_original %>%
  mutate(event_label = as.character(event_label)) %>%
  ggplot(aes(x = billing_postal, y = account_age_days, color = event_label)) +
  geom_point()

fraud_original %>%
  mutate(churn = as.character(event_label)) %>%
  ggplot(aes(x = billing_postal, y = transaction_amt, color = event_label)) +
  labs(title = "Billing Postal and TransactionvAmount") +
  geom_point() 

fraud_original %>%
  mutate(churn = as.character(event_label)) %>%
  ggplot(aes(x = billing_postal, y = transaction_adj_amt, color = event_label)) +
  labs(title = "Billing Postal and Transaction Adjusted Amount") +
  geom_point() 

fraud_original %>%
  mutate(churn = as.character(event_label)) %>%
  ggplot(aes(x = billing_postal, y = historic_velocity, color = event_label)) +
  geom_point() 

fraud_original %>%
  mutate(event = as.character(event_label)) %>%
  ggplot(aes(x = billing_postal, y = days_since_last_logon, color = event_label)) +
  labs(title = "Billing Postal and Days Since Last Logon") +
  geom_point() 

fraud_original %>%
  mutate(event = as.character(event_label)) %>%
  ggplot(aes(x = billing_postal, y = inital_amount, color = event_label)) +
  labs(title = "Billing Postal and Initial Amount") +
  geom_point() 
```

## -- Categorical Data -- 
## (ip_address, user_agent, email_domain, billing_city, billing_state, currency, cvv, signature_image, transaction_type, transaction_env)

```{r}
fraud_original %>%
  group_by(ip_address, event_label) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0) %>%
  mutate(n = `legit` + `fraud`,
         pct_fraud = round(`fraud`/n, 3)) %>%
  arrange(desc(pct_fraud)) -> frequency_table_ip_address

frequency_table_ip_address

fraud_original %>%
  group_by(ip_address, event_label) %>%
  summarise(n = n()) %>%
  ggplot(aes(ip_address), y = n, fill = event_label) + 
  geom_histogram(stat = "count")

fraud_original %>%
  group_by(ip_address, event_label) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(y = reorder(ip_address, n), x = pct, fill = event_label)) + 
  geom_col(position = "fill") 
```

## User Agent (SIGNIFCANT)

## Most common OS is Mozilla 5.0 (fraud rate of about 5.5%)
## Highest fraud rate occurs with use of Opera 8.97 OS (22.6%), next highest being Opera 9.33 (14.5%)

```{r}
fraud_original %>%
  group_by(user_agent, event_label) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0) %>%
  mutate(n = `legit` + `fraud`,
         pct_fraud = round(`fraud`/n, 3)) %>%
  arrange(desc(pct_fraud)) -> user_agent_freq

user_agent_freq
  
fraud_original %>%
  group_by(user_agent, event_label) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(x = reorder(user_agent, n), y = pct, fill = event_label)) + 
  geom_col(position = "fill") +
  labs(title = "User Agent Fraud Distribution")
```

## Email Domain (EXPLORE)
## guerrero-tran.net (n=21, pct=33%), calhoun.org	(n=59, pct=10.2%), crosby.com	(n=57, pct=10.5%)

```{r}
fraud_original %>%
  group_by(email_domain, event_label) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0) %>%
  mutate(n = `legit` + `fraud`,
         pct_fraud = round(`fraud`/n, 3)) %>%
  arrange(desc(n)) -> email_domain_freq

email_domain_freq

fraud_original %>%
  group_by(email_domain, event_label) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = email_domain, x = n, fill = event_label)) + 
  geom_col()

fraud_original %>%
  group_by(email_domain, event_label) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(x = reorder(email_domain, n), y = pct, fill = event_label)) + 
  geom_col(position = "stack") +
  labs(title = "Email Domain Fraud Distribution")

fraud_original %>%
  group_by(email_domain, event_label) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(event_label), y = pct) + 
  geom_histogram(stat = "count") +
  labs(title = "Email Domain Fraud Distribution")
```

## Billing State (SIGNIFICANT)
## Oregon (20.0%, n=5)

```{r}
fraud_original %>%
  group_by(billing_state, event_label) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0) %>%
  mutate(n = `legit` + `fraud`,
         pct_fraud = round(`fraud`/n, 3)) %>%
  arrange(desc(pct_fraud)) -> billing_state_freq

billing_state_freq

fraud_original %>%
  group_by(billing_state, event_label) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = billing_state, x = n, fill = event_label)) + 
  geom_col() +
  labs(title = "Fraud Rate by State")

fraud_original %>%
  group_by(billing_state, event_label) %>%
  summarise(n = n()) %>%
  mutate(pct=n/sum(n)) %>%
  ggplot(aes(y = reorder(billing_state, n), x = pct, fill = event_label)) + 
  geom_col(position = "fill") +
  labs(title = "Fraud Rate by State")

```

## Billing Postal

```{r}
fraud_original %>%
  group_by(billing_postal, event_label) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0) %>%
  mutate(n = `legit` + `fraud`,
         pct_fraud = round(`fraud`/n, 3)) %>%
  arrange(desc(pct_fraud)) -> billing_postal_freq

billing_postal_freq

fraud_original %>%
  group_by(billing_postal, event_label) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = billing_postal, x = n, fill = event_label)) + 
  geom_col()

fraud_original %>%
  group_by(billing_postal, event_label) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(x = reorder(billing_postal, n), y = pct, fill = event_label)) + 
  geom_col(position = "fill") +
  labs(title = "Fraud Rate by Postal Code")
```

## Currency 

## 10.2% of transactions conducted using Euros are fraudulent (unacceptable rate of fraud)
## Operating right at acceptable threshold in US (threshold is 6%, US rate is 6%)
## Canada not as fraudulent (5.1%)

```{r}
fraud_original %>%
  group_by(currency, event_label) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 1) %>%
  mutate(n = `legit` + `fraud`,
         pct_fraud = round(`fraud`/n, 3)) %>%
  arrange(desc(pct_fraud)) -> currency_freq

currency_freq

fraud_original %>%
  group_by(currency, event_label) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = currency, y = n, fill = event_label)) + 
  geom_col() +
  labs(title = "Fraud Rate by Currency")

fraud_original %>%
  group_by(currency, event_label) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(x = reorder(currency, n), y = pct, fill = event_label)) + 
  geom_col(position = "fill") +
  labs(title = "Fraud Rate by Currency")
```

## CVV

```{r}
fraud_original %>%
  group_by(cvv, event_label) %>%
  summarise(n = n())  %>%
  pivot_wider(names_from = event_label, values_from = n, values_fill = 1) %>%
  mutate(n = `legit` + `fraud`,
         pct_fraud = round(`fraud`/n, 3)) %>%
  arrange(desc(pct_fraud)) -> frequency_table_cvv

frequency_table_cvv

fraud_original %>%
  group_by(cvv, event_label) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = cvv, y = n, fill = event_label)) + 
  geom_col() +
  labs(title = "Fraud Rate by CVV Category")

fraud_original %>%
  group_by(cvv, event_label) %>%
  summarise(n = n()) %>%
  mutate(pct = n/sum(n)) %>%
  ggplot(aes(x = reorder(cvv, n), y = pct, fill = event_label)) + 
  geom_col(position = "fill") +
  labs(title = "Fraud Rate by CVV Category")
```


```{r}
category_eval <- function(col){
  
fraud_training %>% 
  group_by(event_label) %>%
  count(!!as.name(col)) %>%
  pivot_wider(values_from=c(n), names_from = event_label) %>%
      mutate(pct_1 = `fraud`/ (`legit` + `fraud`),
             pct_0 = 1 - pct_1) %>%
    arrange(desc(pct_1)) %>%
    print()
}

for (col in colnames(fraud_training %>% select_if(is.factor))){
  print(col)
  category_eval(col)
}

char_explore <- function(col) {
   organics %>%
     ggplot(., aes(!!as.name(col))) +
     geom_bar(aes(fill = event_label), position = "fill")
}
```

```{r}
category_eval_gini <- function(col){
  
fraud_training %>% 
  group_by(event_label) %>%
  count(!!as.name(col)) %>%
  pivot_wider(values_from=c(n), names_from = event_label) %>%
      mutate(pct_1 = `fraud`/ (`legit` + `fraud`),
             pct_0 = 1 - pct_1) %>%
    mutate(gini_x = 2*pct_1*pct_0,
           entropy_x = -pct_1*log(pct_1,2)  -pct_0*log(pct_0,2)) %>%
    arrange(desc(pct_1)) %>%
    print()
}

for (col in colnames(fraud_training %>% select_if(is.factor))){
  print(col)
  category_eval_gini(col)
}
```

```{r}
fraud_comparison <- fraud_comparison %>%
  dplyr::select(event_id, account_age_days, transaction_amt, transaction_adj_amt, historic_velocity, user_agent, billing_city, billing_state, card_bin, currency, days_since_last_logon, inital_amount, event_label, email_domain_pct_fraud, billing_postal_pct_fraud, cvv_pct_fraud, signature_pct_fraud, transaction_type_pct_fraud, transaction_env_pct_fraud, transaction_initiate_pct_fraud)
```


## Train/Test Split

```{r}
set.seed(100)

split1 <- initial_split(fraud_comparison, prop = 0.7, strata = event_label)

train <- training(split1)
test <- testing(split1)

# -- kfold -- 
train_kfolds <- vfold_cv(train, v = 5)

sprintf("Train PCT : %1.2f%%", nrow(train)/ nrow(fraud_training) * 100)
sprintf("Test  PCT : %1.2f%%", nrow(test)/ nrow(fraud_training) * 100)
```

## Logistic Recipe

```{r}
logistic_recipe <- recipe(event_label ~ ., data = train) %>%
  step_rm(event_id, billing_city) %>%
  step_impute_median(all_numeric(), -all_outcomes()) %>%
  step_unknown(all_nominal(), -all_outcomes()) %>%
  step_dummy (all_nominal(), -all_outcomes()) %>%
  prep()
logistic_recipe
```

## Logistic Model

```{r}
logistic_model <- logistic_reg(penalty = 0.01, mixture = 1) %>%
  set_mode("classification") %>%
  set_engine("glm")

logistic_wf <- workflow() %>%
  add_recipe(logistic_recipe) %>%
  add_model(logistic_model) %>%
  fit(train)

logistic_wf %>%
  pull_workflow_fit() %>%
  tidy() %>%
  mutate_at(c("estimate", "std.error", "statistic", "p.value"), round, 10) %>%
  mutate(across(is.numeric, round, 3))

logistic_wf %>%
  pull_workflow_fit() %>%
  vip()

logistic_fit <- logistic_wf %>%
  fit(data = train)
```

## Logistic Predictions

```{r}
# -- deal w. the first event issue -- # 
options(yardstick.event_first = FALSE)
predict(logistic_wf, train, type = "prob") %>%
  bind_cols(predict(logistic_wf, train, type = "class")) %>%
  bind_cols(train) %>%
  metrics(event_label, estimate = .pred_class, .pred_fraud)

predict(logistic_wf, test, type = "prob") %>%
  bind_cols(predict(logistic_wf, test, type = "class")) %>%
  bind_cols(test) -> logistic_test 

logistic_test %>%
    metrics(event_label, estimate = .pred_class, .pred_fraud)
```

## Decision Tree Recipe

```{r}
tree_recipe <- recipe(event_label ~ ., data = train) %>%
  step_rm(event_id, billing_city) %>%
  step_impute_median(all_numeric(), -all_outcomes()) %>%
  step_unknown(all_nominal(), -all_outcomes()) %>%
  step_dummy (all_nominal(), -all_outcomes()) %>%
  prep()
tree_recipe
```

## Decision Tree Model

```{r}
tree_spec <- decision_tree(c=0) %>%
  set_mode("classification") %>%
  set_engine("rpart")

tree_wf <- workflow() %>%
  add_recipe(tree_recipe) %>%
  add_model(tree_spec) %>%
  fit(train)

tree_wf %>%
  pull_workflow_fit() %>%
  vip()
```

## Decision Tree Predictions

```{r}
# -- deal w. the first event issue -- # 
options(yardstick.event_first = FALSE)
predict(tree_wf, train, type = "prob") %>%
  bind_cols(predict(tree_wf, train, type = "class")) %>%
  bind_cols(train) %>%
  metrics(event_label, estimate = .pred_class, .pred_fraud)

predict(tree_wf, test, type = "prob") %>%
  bind_cols(predict(tree_wf, test, type = "class")) %>%
  bind_cols(test) -> tree_test 

tree_test %>%
  metrics(event_label, estimate = .pred_class, .pred_fraud)
```

## RF 

```{r}
rf_recipe <- recipe(event_label ~ ., data = train) %>%
  step_rm(event_id, billing_city) %>%
  step_impute_median(all_numeric(), -all_outcomes()) %>%
  step_unknown(all_nominal(), -all_outcomes()) %>%
  step_dummy (all_nominal(), -all_outcomes()) %>%
  prep()
rf_recipe
```

```{r}
rf_model <- rand_forest(
  trees = 100,
  min_n = 10) %>%
  set_engine("ranger",
            importance = "permutation",
            max.depth  = 50) %>% 
  set_mode("classification")
  
#Permutation

rf_workflow <- workflow() %>% 
  add_recipe(rf_recipe) %>%
  add_model(rf_model)  

rf_fit <- rf_workflow %>%
  fit(data = train)
```

```{r}
rf_tune_grid <- grid_regular(trees(c(100,200)),
                          min_n(),
                          levels = 2)

print(rf_tune_grid)
```

```{r}
all_cores <- detectCores(logical = TRUE)
sprintf("# of Logical Cores: %d", all_cores)

cl <- makeCluster(all_cores)

registerDoParallel(cl)
    
# -- k-fold RF
rf_tuning_results <- 
  rf_workflow %>% 
  tune_grid(
    resamples = train_kfolds,
    grid = rf_tune_grid)

rf_tuning_results %>% 
  collect_metrics() %>%
  mutate_if(is.numeric, round,3) %>% 
  pivot_wider(names_from = .metric, values_from=c(mean, std_err))
```

## -- Evaluate -- 

```{r}
#Score (training)  
predict(rf_fit, train, type = "prob") %>%
  bind_cols(predict(rf_fit, train, type = "class")) %>%
  bind_cols(., train) -> scored_train

#Score (testing) 
predict(rf_fit, test, type = "prob") %>%
  bind_cols(predict(rf_fit, test, type = "class")) %>%
  bind_cols(., test) -> scored_test  

#Metrics: Train/Test 
scored_train %>% 
  metrics(event_label, `.pred_fraud`, estimate = .pred_class) %>%
  mutate(part = "training") %>%
  bind_rows(scored_test %>%
              metrics(event_label, `.pred_fraud`, estimate = .pred_class) %>%
              mutate(part = "testing") ) %>%
  filter(.metric %in% c('accuracy', 'roc_auc')) %>%
  pivot_wider(names_from = .metric, values_from = .estimate)
  
#VIP: top 10
rf_fit %>%
  extract_fit_parsnip() %>%
  vip(num_features = 10)
  
#Confusion Matrices
scored_train %>%
  conf_mat(event_label, .pred_class) %>%
  autoplot(type = "heatmap")
  
 scored_test %>%
  conf_mat(event_label, .pred_class) %>%
  autoplot(type = "heatmap")
   
options(yardstick.event_first = FALSE)

#ROC-AUC 
scored_train %>%
mutate(model = "train") %>%
bind_rows(scored_test %>%
            mutate(model = "test")) %>%
group_by(model) %>%
roc_curve(event_label, `.pred_fraud`) %>%
autoplot() 

#Operating Range 
scored_test  %>%
roc_curve(event_label, `.pred_fraud`) %>%
mutate(FPR = round((1 - specificity), 2),
       TPR = round(sensitivity, 3),
       score_threshold =  1 - round(.threshold, 3)) %>%
group_by(FPR) %>%
summarise(score_threshold = max(score_threshold),
          TPR = max(TPR)) %>%
  ungroup() %>%
  mutate(precision = TPR/(TPR + FPR)) %>%
  subset(select = c("FPR", "TPR", "precision", "score_threshold")) %>%
  filter(FPR <= 0.2) 

precision(scored_test, event_label, .pred_class)
recall(scored_test, event_label, .pred_class)
```

## Holdout Preds

```{r, warning=FALSE, message=FALSE}
#Score Training
predict(logistic_fit, fraud_holdout, type = "prob") %>%
  bind_cols(predict(logistic_fit, fraud_holdout, type = "class")) %>%
  bind_cols(., fraud_holdout) -> holdout_scored

holdout_scored %>%
  ggplot(aes(.pred_fraud, fill = .pred_class)) +
  geom_histogram(bins = 100) +
  xlim(0, 1) +
  geom_vline(aes(xintercept = 0.06)) +
  labs(title = "Prediction File Score Distribution")

holdout <- holdout_scored %>%
  mutate(event_label = as.factor(if_else(.pred_fraud >= 0.06, 1, 0))) %>%
  subset(select = c("event_id", "event_label"))

write_csv(holdout, "holdout_scored.csv")

precision(holdout, .pred_class)
recall(holdout, .pred_class)
```
